Approximate Code: A Cost-Effective Erasure Coding Framework for Tiered Video Storage in Cloud Systems

### 2019-04-23 ApproximateCode.tex
version 4.5

\begin{abstract}
Nowadays massive video data is stored in cloud storage systems, which are generated by various applications such as autonomous driving, news media, security monitoring, etc. Meanwhile, erasure coding is a popular technique in cloud storage to provide both high reliability with low monetary cost, where triple disk failure tolerant arrays (3DFTs) is a typical choice. Therefore, how to minimize the storage cost of video data in 3DFTs is challenge for cloud storage systems. Although there are several solutions like approximate storage technique, they cannot guarantee low storage cost and high data reliability concurrently.

@@

To reduce the storage cost in cloud storage systems, a feasible solution is approximate storage. Approximate storage exposes unimportant data to errors, saving the overhead of redundant backups \cite{niklaus2018context, sampson2014approximate} , thus the data reliability cannot be guaranteed.
The second solution is using disk arrays like RAID-5 or RAID-6 \cite{RAID}, but the capability of fault tolerance are sacrificed.
Data compression\footnote{Typically, video coding (e.g., H.264 \cite{wiegand2003overview}) is a special type of data compression.}
is the third strategy to reduce the storage overhead \cite{ziv1977universal, ziv1978compression, deutsch1996deflate}, which needs to be collaborated with erasure codes for high reliability. However, the compression/decompression processes result in a large amount of computational overhead, which limits their usage in cloud systems. 
Therefore, existing solutions cannot provide low storage cost and high reliability simultaneously.

@@

We have the following contributions of this work,
\begin{enumerate}
\item We propose Approximate Code, which a cost-effective framework to store video data in cloud storage systems.
\item Approximate Code can be implemented by combining various erasure codes in 3DFTs, such as RS, STAR Code, TIP-Code, etc.
\item We conduct several quantitative analysis, simulations and experiments according to different layouts of various erasure codes, and the results show that Approximate Code achieves lower storage cost and faster data recovery when single disk fails.
\end{enumerate}

@@

H.264 classifies all frames into three different categories:
\begin{enumerate}
    \item I frame: A frame that is not depend on other frame data, which means it can be decoded independently of other frames.
    \item P frame: A frame holds the changes compared to the previous frame, which saves the storage space by leaving out redundant information.
    \item B frame: A frame decreases the storage space as well by utilizing the data of both the preceding and following frames.
\end{enumerate}
A group of pictures (GOP) consists of one I frame followed by a number of consecutive P and B frames, as shown in Figure \ref{H264-IPB}.
Within each GOP, the I frame is the most significant because all other frames rely on if for recovery. P frames are the second important, and B frames have the least value.
Based on this feature, a special program can be designed to distinguish the importance of video frames.

@@

Local Construction Code (LRC) \cite{LRC} 
is shown in Figure \ref{fig-LRC-1}. It divides the data nodes into several groups, which are called local stripes. Typically, each local stripe contains one parity node, which is calculated via the data nodes in the same stripe. Global stripe is generated via crossing multiple local stripes.

\begin{figure}
\centering
\subfigure[\textbf{RS Code:} Horizontal parity coding (e.g., $C_{0,5} = \sum_{i=0}^3 A_{0,i}C_{0,i}$)]{
    \includegraphics[width=0.92\linewidth]{photo/RS-1.pdf}\label{fig-RS-1}
}

\subfigure[\textbf{LRC Code:} Horizontal parity coding (e.g., the local parity $C_{0,5} = \sum_{i=2}^3 A_{0,i}C_{0,i}$ and the global parity $C_{0,7} = \sum_{i=0}^3 A_{0,i}C_{0,i}$)]{
    \includegraphics[width=0.8\linewidth]{photo/LRC-1.pdf}\label{fig-LRC-1}
}\vspace{-3mm}
\caption{Encoding of RS code and LRC}
\vspace{-3mm}
\end{figure}

STAR code \cite{STAR} is an extension of EVENODD \cite{EVENODD} code, as shown in Figure \ref{fig-star-tip}.

In the encoding process of STAR code, the generation of diagonal parity and anti-diagonal parity requires to calculate $S1$ and $S2$ first, which lead to a long parity chain.

\begin{figure}[!ht]
\centering
\subfigure[\textbf{STAR Code:} Horizontal parity coding (e.g., $C_{0,5} = C_{0,0} \oplus C_{0,1} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4}$).]{
\includegraphics[width=0.42\linewidth]{photo/star-hori.pdf}\label{fig-star-1}
}
\hspace{5pt}
\subfigure[\textbf{STAR Code:} Diagonal parity coding (e.g., $S_1 = C_{3,1} \oplus C_{2,2} \oplus C_{1,3} \oplus C_{0,4}$ and $C_{0,6} = C_{0,0} \oplus C_{3,2} \oplus C_{2,3} \oplus C_{1,4} \oplus S_1$).]{
\includegraphics[width=0.42\linewidth]{photo/star-diag.pdf}\label{fig-star-2}
}

\subfigure[\textbf{STAR Code:} Anti-diagonal parity coding (e.g., $S_2 = C_{0,1} \oplus C_{1,2} \oplus C_{2,3} \oplus C_{3,4}$ and $C_{0,7} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{3,3} \oplus S_2$).]{
\includegraphics[width=0.42\linewidth]{photo/star-anti.pdf}\label{fig-star-3}
}
\hspace{5pt}
\subfigure[\textbf{TIP-Code:} Horizontal parity coding (e.g., $C_{0,7} = C_{0,0} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4} \oplus C_{0,5}$).]{
\includegraphics[height=2.5cm]{photo/tip-hori.pdf}\label{fig-tip-1}
}

\subfigure[\textbf{TIP-Code:} Diagonal parity coding (e.g., $C_{0,1} = C_{0,0} \oplus C_{5,2} \oplus C_{4,3} \oplus C_{2,5} \oplus C_{1,6}$ ).]{
\includegraphics[height=2.5cm]{photo/tip-diag.pdf}\label{fig-tip-2}
}
\hspace{5pt}
\subfigure[\textbf{TIP-Code:} Anti-diagonal parity coding (e.g., $C_{0,6} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{4,4} \oplus C_{5,5}$).]{
\includegraphics[height=2.5cm]{photo/tip-anti.pdf}\label{fig-tip-3}
}
\caption{Encoding of STAR (Figure \ref{fig-star-1}, \ref{fig-star-2} and \ref{fig-star-3}) and TIP (Figure \ref{fig-tip-1}, \ref{fig-tip-2} and \ref{fig-tip-3}) code ($p = 5$). Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape.}
\label{fig-star-tip}
\end{figure}

TIP-Code is also an XOR-based 3DFTs erasure code.
Compared with STAR code, the encoding and data arrangement of TIP-Code eliminates the need to repeatedly calculate elements $S1$ and $S2$, so its cost of updating a single block is less than STAR code.

STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$, where $p$ is a prime number.

\subsection{Approximate Storage \textcolor[rgb]{1.00,0.00,0.00}{Compression}}
%Storage techniques nowadays generally regard all information of the same importance, which causes significant costs in energy, disk drives and computing resources. But not all data need high-reliability storage for its backup. That is why the concept of approximate storage is introduced.
Approximate Storage is an innovative approach of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.

@@

\iffalse
\begin{table}[ht]\footnotesize
\centering
\caption{
Comparison of storage overhead, reliability and performance among various storage methods for video files}\label{tab-AS-EC-AP}
\begin{tabular}{|c|c|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|}
\hline
\multirow{2}{*}{EC} & RS & high & high & high \\ \cline{2-5}
 & RAID-6 & medium & medium & medium \\ \hline
\multicolumn{2}{|c|}{Approximate Storage} & low & low & low \\ \hline
\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Approximate\\ Code\end{tabular}} & ID & low & high & low \\ \cline{2-5}
 & UD & low & medium & low \\ \hline
\multicolumn{2}{|c|}{Data Compression} & low & / & high \\ \hline
\end{tabular}
\end{table}
\fi

@@

\subsection{Our Motivation}

From the summary of Table \ref{tab-AS-EC-AP}, the device level scheme of existing 3DFTs has high storage overhead, while RAID-5 or RAID-6 maintains medium storage overhead but sacrifice fault tolerance. Although approximate storage achieves low cost, its reliability cannot be satisfied in cloud environment. Application layer methods such as compression algorithms have high computational overhead and need to be used together with erasure codes to ensure reliability.
Therefore, the existing solution cannot guarantee high reliability and low overhead at the same time of video storage.

A feasible solution is combining the existing solutions together with tiered storage \cite{krish2014hats} \cite{wang2014balancing} \cite{zhang2010automated} \cite{udipi2012lot}, which motivates us to propose Approximate Code.

@@

\subsubsection{Code Input}
Acquire an erasure coding input and get the corresponding parameters. Typically, for cloud storage systems, erasure codes used in 3DFTs are accepted by Approximate Code. Several parameters related to erasure codes need to be collected, such as the number of data nodes $k$ and the number of parity nodes $r$.

\subsubsection{Code Segmentation}
For an inputted erasure code, we assume that its fault tolerance is $x$. The Approximate Code first splits its parities into two parts: local and global parities. The former verifies all important and non-critical data, while the latter only verifies important data. Code segmentation are designed to ensure that local parities can tolerate any $r$ node failures, so the fault tolerance of non-critical data is $r$. For important data, the code segmentation ensures that the parity block of important data can be completely recombined into the original $x$DFTs erasure code scheme.

For example, several erasure codes in 3DFTs like STAR have three types of parities, horizontal, diagonal and anti-diagonal parities. In the code segmentation step, the horizontal parities are separated from other two parities.

\subsubsection{Structure Selection}
The Approximate Code framework then choose the structure for the input erasure code.
There are two main structures that distribute important and unimportant data in different ways.
As shown in Figure \ref{fig-framework}, in Even structure, important data occupies 1 block in each node, and in Uneven structure, it occupies 1 data stripe.
We specify that in Even structure, the ratio of important data to each node is $1/h$, thereby ensuring that the number of important data in both Even structure and Uneven structure just fills up $k$ nodes.

Since Even structure distributes important data across each node, it guarantees a more balanced load. Uneven structure concentrates important data into a stripe, and provides greater reliability for important data. A detailed analysis of this will be presented in Section \ref{ReconstructionFT}.

\subsubsection{Code Generation}\label{code-gen}
After code segmentation and structure selection, the Approximate Code Framework generates an approximate form of the input erasure code.
The construction of the Approximate Code is determined by 5 parameters $k$, $r$, $g$, $h$ and Structure.

We define the naming rules of the output Approximate Code as \textbf{APPR.CodeName} ($k,r,g,h$,Structure), where ``CodeName'' is the name of the input erasure code. Paremeter $Structure$ is Even or Uneven and it can be omitted when not focusing on the specific construction.

In a $n$-node stripe, $k$ of them are data nodes and $r=n-k$ nodes are for local parity, where each node can be divided into multiple blocks.
Approximate Code are designed for $h$ stripes, therefore it includes $k*h$ data nodes and $r*h$ local parity nodes.
Besides them, $g$ nodes are designed for global parity, which are calculated only by the important data blocks, so the total number of nodes $N$ in Approximate Code ($k,r,g,h$) is
$N= h*(k+r) + g$.

Approximate Code guarantees that the unimportant data can tolerate any $r$ node failures and the important data can tolerate any $r+g$ node failures.
Since the 3DFTs is a tipical configuration, we mainly discuss the situation of $r+g=3$, so $r$ is usually 1 or 2.

\subsection{Approximate RS-based Codes}
For RS($k,p$), it can be seen that it provides $p$ independent horizontal parity nodes for $k$ data nodes. Therefore, the code segmentation for RS is arbitrary, that is, it supports any $r=p-g(0<g<p)$. RS also supports both two structures.

For the situation shown in Figure \ref{fig-framework}, we consider the input erasure code as RS($4,3$). It is divided into two local parities and one global parities with the Uneven structure and it generate Approximate RS Code ($4,2,1,3$,Uneven).
As a result, the unimportant data constitutes RS($4,2$), and the important data constitutes RS($4,3$).

\begin{figure}
    \centering
    \subfigure[XXX]{
        \includegraphics[width=0.8\linewidth]{photo/RS-2.pdf}\label{fig-RS-2}
    }

    \subfigure[XXX]{
        \includegraphics[width=0.8\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
    }
    \caption{The construction and the encoding process of APPR.RS ($4,1,2,3$)}
\end{figure}

\subsection{Approximate XOR-based Codes}
Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several XOR-based codes to provide faster encoding and reconstruction speed than RS. This section introduce two tipical construction of Approximate XOR-based Code, Approximate STAR Code and Approximate TIP-Code.

@@

\subfigure[Generation process]{
    \label{fig-ap-tip-GEN}
    \includegraphics[width = \linewidth]{photo/APPR-STAR-GEN.pdf}
}
\caption{The construction and the encoding process of APPR.STAR ($5,2,1,4$,Uneven), which can be divided into STAR (encode important data) and EVENODD (encode unimportant data).}
\label{fig-ap-5214}
\end{figure}

\subsubsection{Approximate STAR Code}
Figure \ref{fig-ap-5214} shows the construction and the encoding process of APPR.STAR($5,2,1,4$,Uneven).
As introduced in \ref{existEC}, STAR Code \cite{STAR} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
Since STAR is a direct extension of EVENODD\cite{EVENODD}, that is to say, STAR code that removes the anti-diagonal parity is the typical RAID-6 code EVENODD. As shown in Figure \ref{fig-ap-5214}, in this case, the horizontal and diagonal parity are used as local parities while the anti-diagonal parity is defined as global parity.
According to the construction requirements of STAR, each node is divided into 4 blocks.

@@

\begin{table}[htb]
\centering
\caption{Comparison of storage overhead, fault tolerance and average single write performance between RS, STAR, TIP, Approximate RS, Approximate STAR and Approximate TIP, where $p$ is a prime number.}\label{tab-properties}
\begin{tabular}{|c|c|c|c|}
\hline
EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault\\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Ave Single Write\\ Overhead \end{tabular} \\ \hline
RS($k,r$) & $(k+r)/k$ & $r$ & $r+1$ \\ \hline
STAR($p$) & $(p+3)/p$ & $3$ & $6-\frac{4}{p}$ \\ \hline
TIP-code($p$) & $\frac{p+1}{P-2}$ & $3$ & 4 \\ \hline
\begin{tabular}[c]{@{}c@{}}APPR.RS\\ ($k,r,g,h$)\end{tabular} & \multirow{3}{*}{$\frac{(k+r)h+g}{kh}$} & $r+g$ & $1+r+\frac{g}{h}$ \\ \cline{1-1} \cline{3-4}
\begin{tabular}[c]{@{}c@{}}APPR.STAR\\ ($k,2,1,h$)\end{tabular} &  & 3 & $2\frac{k-h-1}{kh}+4$ \\ \cline{1-1} \cline{3-4}
\begin{tabular}[c]{@{}c@{}}APPR.TIP\\ ($k,1,2,h$)\end{tabular} &  & 3 & $2+\frac{2}{h}$ \\ \hline
\end{tabular}
\end{table}

@@

To compared with Approximate Code, We choose several 3DFTs erasure codes, including RS code, LRC, STAR and TIP-Code.
Experiments as well as mathematical analysis are used to demonstrate the performance of Approximate Code.

To prove that the lost of unimportant data is acceptable, we use the latest interpolation algorithm to simulate the approximate recovery and fuzzification process in a data corruption scenario.

\subsubsection{Metrics and Methods for Mathematical Analysis: }
We use the \textbf{Storage Efficiency}, \textbf{Fault Tolerance} and \textbf{Single Write(update) Cost} defined in Table \ref{tab-properties} as measure.
We first analyze the impact of the settings of the three parameters on these metrics, then we compare these matrics with several EC methods.

\subsubsection{Metrics and Methods for Experiments: }
We use \textbf{Encoding Time} and \textbf{Recovery Time} as the metrics in our experiments. Encoding Time is the time for generating all parity nodes and Recovery Time is the time for recovering the lost nodes.

In our experiments of recovery time, we compare Approximate Code with several other codes with the same data nodes $k$.
Note that the Approximate Code can only recover important data in some cases, and we don't consider the recovery of non-critical data, so the Approximate Code may recover less data than other codes.

The environment of our experiments are shown in Table \ref{tab-platform}. We set a Hadoop system with one NameNode and $h$ DataNodes. Each DataNodes storage the data of one layer of Approximate Code and the global parities are distributed at each DataNodes. We set $h=4,6$ and node size equal $1GB$ here as two default configurations.

Our experiment can mainly be divided into four cases. First, we evaluate the encoding time for several erasure codes. We then evaluate the recovery time of the scenarios where single, double and triple nodes are corrupted.

\subsubsection{\textcolor{red}{Metrics and Methods for Frame Recovery: }}
we performed the experiment of video frame recovery with the frame interpolation technique. The dataset we used is a collection of 60fps videos from \textbf{YouTube-8m} \cite{youtube8m}. We simulated a 1\% data loss\footnote{In a distributed system, a single video can be stored in dozens or even hundreds of nodes. We assume that its important data is recovered, while the loss of unimportant data accounts for 1\% of the total video size.} on the less important video frames and successfully recovered the lost ones, although the recovered frames have some discrepancies with the original data. The average quality of the recovered pictures is commonly above 35dB in terms of Peak Signal to Noise Ratio PSNR .

>>>>

\begin{abstract}
Nowadays massive video data are stored in cloud storage systems, which are generated by various applications such as autonomous driving, news media, security monitoring, etc. Meanwhile, erasure coding is a popular technique in cloud storage to provide both high reliability with low monetary cost, where triple disk failure tolerant arrays (3DFTs) is a typical choice. Therefore, how to minimize the storage cost of video data in 3DFTs is challenge for cloud storage systems. Although there are several solutions like approximate storage technique, they cannot guarantee low storage cost and high data reliability concurrently.

@@

To reduce the storage cost in cloud storage systems, a feasible solution is approximate storage. Approximate storage exposes unimportant data to errors, saving the overhead of redundant backups \cite{niklaus2018context, sampson2014approximate} , thus the data reliability cannot be guaranteed.
The second solution is using disk arrays like RAID-5 or RAID-6 \cite{RAID}, but the capability of fault tolerance are sacrificed.
Data compression\footnote{Typically, video coding (e.g., H.264 \cite{wiegand2003overview}) is a special type of data compression.}
is the third strategy to reduce the storage overhead \cite{ziv1977universal, ziv1978compression, deutsch1996deflate}, which needs to be collaborated with erasure codes for high reliability. However, the compression/decompression processes result in a large amount of computational overhead, which limits their usage in cloud systems. 
Therefore, existing solutions are difficult to provide low storage cost and high reliability simultaneously.

@@

We have the following contributions of this work,
\begin{enumerate}
\item We propose Approximate Code, which a cost-effective framework to store video data in cloud storage systems.
\item Approximate Code can be implemented by combining various erasure codes in 3DFTs, such as RS, STAR Code, TIP-Code, etc.
\item We conduct several quantitative analysis, simulations and experiments according to different layouts of various erasure codes, and the results show that Approximate Code achieves a small number of parities, low storage cost, high single write performance, and fast data recovery under various failure scenarios.
\end{enumerate}

@@

H.264 classifies all frames into three different categories:
\begin{enumerate}
    \item I frame: A frame that is self-contained, which means it can be decoded independently.
    \item P frame: A frame holds the changes compared to the previous frame, which saves the storage space by leaving out redundant information.
    \item B frame: A frame decreases the storage space as well by utilizing the data of both the preceding and following frames.
\end{enumerate}
A group of pictures (GOP) consists of one I frame followed by a number of consecutive P and B frames, as shown in Figure \ref{H264-IPB}.
Within each GOP, the I frame is the most significant because all other frames rely on if for recovery. P frames are the second important, and B frames have the least value.
Based on this feature, a special program can be designed to distinguish the importance of video frames.

@@

Local Construction Code (LRC) \cite{LRC} 
is shown in Figure \ref{fig-LRC-1}. It divides the data nodes into several groups, which are called local stripes. Typically, each local stripe contains one local parity node, which is calculated via the data nodes in the same stripe. Global stripe is generated via crossing multiple local stripes.

\begin{figure}
\centering
\subfigure[RS Code for arbitrary storage nodes ($k=4, r=3$). The figure shows the encoding of different horizontal parities. (e.g., $C_{0,5} = \sum_{i=0}^3 A_{0,i}C_{0,i}$)]{
    \includegraphics[width=0.92\linewidth]{photo/RS-1.pdf}\label{fig-RS-1}
}

\subfigure[LRC Code for arbitrary storage nodes ($k=4, r=2, g=2$), where 4 nodes are divided into 2 local groups and each of them has a local parity.The figure shows the encoding of local and global parities. (e.g., the local parity $C_{0,5} = \sum_{i=2}^3 A_{0,i}C_{0,i}$ and the global parity $C_{0,7} = \sum_{i=0}^3 A_{0,i}C_{0,i}$)]{
    \includegraphics[width=0.8\linewidth]{photo/LRC-1.pdf}\label{fig-LRC-1}
}\vspace{-3mm}
\caption{Encoding of RS code and LRC}
\vspace{-3mm}
\end{figure}

STAR code \cite{STAR} is an extension of EVENODD \cite{EVENODD} code, as shown in Figure \ref{fig-star-tip}.
In the encoding process of STAR code, the generation of diagonal parity and anti-diagonal parity requires to calculate $S1$ and $S2$ first, which lead to a long parity chain.

\begin{figure}[!ht]
\centering
\subfigure[\textbf{STAR Code:} Horizontal parity coding (e.g., $C_{0,5} = C_{0,0} \oplus C_{0,1} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4}$).]{
\includegraphics[width=0.42\linewidth]{photo/star-hori.pdf}\label{fig-star-1}
}
\hspace{5pt}
\subfigure[\textbf{STAR Code:} Diagonal parity coding (e.g., $S_1 = C_{3,1} \oplus C_{2,2} \oplus C_{1,3} \oplus C_{0,4}$ and $C_{0,6} = C_{0,0} \oplus C_{3,2} \oplus C_{2,3} \oplus C_{1,4} \oplus S_1$).]{
\includegraphics[width=0.42\linewidth]{photo/star-diag.pdf}\label{fig-star-2}
}
\vspace{-3mm}
\subfigure[\textbf{STAR Code:} Anti-diagonal parity coding (e.g., $S_2 = C_{0,1} \oplus C_{1,2} \oplus C_{2,3} \oplus C_{3,4}$ and $C_{0,7} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{3,3} \oplus S_2$).]{
\includegraphics[width=0.42\linewidth]{photo/star-anti.pdf}\label{fig-star-3}
}
\hspace{5pt}
\subfigure[\textbf{TIP-Code:} Horizontal parity coding (e.g., $C_{0,7} = C_{0,0} \oplus C_{0,2} \oplus C_{0,3} \oplus C_{0,4} \oplus C_{0,5}$).]{
\includegraphics[height=2.5cm]{photo/tip-hori.pdf}\label{fig-tip-1}
}
\vspace{-3mm}
\subfigure[\textbf{TIP-Code:} Diagonal parity coding (e.g., $C_{0,1} = C_{0,0} \oplus C_{5,2} \oplus C_{4,3} \oplus C_{2,5} \oplus C_{1,6}$ ).]{
\includegraphics[height=2.5cm]{photo/tip-diag.pdf}\label{fig-tip-2}
}
\hspace{5pt}
\subfigure[\textbf{TIP-Code:} Anti-diagonal parity coding (e.g., $C_{0,6} = C_{0,0} \oplus C_{1,1} \oplus C_{2,2} \oplus C_{4,4} \oplus C_{5,5}$).]{
\includegraphics[height=2.5cm]{photo/tip-anti.pdf}\label{fig-tip-3}
}\vspace{-3mm}
\caption{\small{Encoding of STAR (Figure \ref{fig-star-1}, \ref{fig-star-2} and \ref{fig-star-3}) and TIP (Figure \ref{fig-tip-1}, \ref{fig-tip-2} and \ref{fig-tip-3}) code ($p = 5$). Each column represents a node, each block represents an element, and parity chains are represented by elements with same shape. STAR requires the number of data nodes to be $p$, and TIP requires that to be $p-2$, where $p$ is a prime number.}}
\vspace{-3mm}
\label{fig-star-tip}
\end{figure}

TIP-Code is also an XOR-based 3DFTs erasure code.
Compared with STAR code, the parities are generated independently, which reduces the number of I/O operations for partial stripe writes.

\subsection{Approximate Storage}
%Storage techniques nowadays generally regard all information of the same importance, which causes significant costs in energy, disk drives and computing resources. But not all data need high-reliability storage for its backup. That is why the concept of approximate storage is introduced.
Approximate Storage is an innovative approach of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.

@@

@@

\subsection{Our Motivation}
We summarize various methods to reduce storage cost for video files in Table \ref{tab-AS-EC-AP}, the device level scheme of existing 3DFTs has high storage overhead, while RAID-5 or RAID-6 maintains medium storage overhead but sacrifice fault tolerance. Although approximate storage achieves low cost, its reliability cannot be satisfied in cloud environment. Application layer methods such as compression algorithms have high computational overhead and need to be used together with erasure codes to ensure reliability.
Therefore, the existing solution cannot guarantee high reliability and low overhead at the same time of video storage.

From the summary of Table \ref{tab-AS-EC-AP}, existing solutions have their drawbacks on providing high reliability with low storage cost. 
A feasible solution is combining various erasure codes with tiered storage \cite{krish2014hats} \cite{wang2014balancing} \cite{zhang2010automated} \cite{udipi2012lot}, which motivates us to propose Approximate Code.

@@

\subsubsection{Code Input}
Acquire an erasure coding input and get the corresponding parameters. Typically, for cloud storage systems, erasure codes used in 3DFTs are accepted as the input. Several parameters related to erasure codes need to be collected, such as the number of data nodes $k$ and the number of parity nodes $r$.

\subsubsection{Code Segmentation}
For an inputted erasure code, we assume that its fault tolerance is $x$. The Approximate Code first splits its parities into two parts, local and global parities. The local parities are used for all data, while the global parities focus on the important data. Code segmentation are designed to ensure that local parities can tolerate any $r$ node failures, so the fault tolerance of unimportant data is $r$. For important data, the code segmentation ensures that the important data have the capabilities of fault tolerance by up to $x$ nodes.

For example, several erasure codes in 3DFTs like STAR have three types of parities, horizontal, diagonal and anti-diagonal parities. In the code segmentation step, the horizontal parities are regarded as local parities, which are separated from the diagonal/anti-diagonal parities (shown in Fig. \ref{fig-appr-star} and illustrated in \ref{APPRXOR} in detail).

\subsubsection{Structure Selection}
The framework choose the structure after code segmentation.
There are two main structures that distribute important and unimportant data in different ways.
As shown in Figure \ref{fig-framework}, in Even structure, important data are distributed uniformly among all data nodes. The other structure is Uneven structure, which stores the important data among several nodes dedicatedly.
%We specify that in Even structure, the ratio of important data to each node is $1/h$, thereby ensuring that the number of important data in both Even structure and Uneven structure just fills up $k$ nodes.

Since Even structure distributes important data across each node, it guarantees a balanced workload. Uneven structure concentrates important data into several dedicated nodes, and provides better reliability based on failure locality. \textcolor{red}{[CITE FAILURE MODEL]}.

\subsubsection{Code Generation}\label{code-gen}
After code segmentation and structure selection, the Approximate Code Framework generates an approximate form of the inputted erasure code.
The construction of the Approximate Code is determined by 4 parameters $k$, $r$, $g$, $h$ and the structure type.

We define the output Approximate Code as \textbf{APPR.CodeName ($k,r,g,h$, Structure Type)}, where ``CodeName'' is the name of the input erasure code. Structure type is Even or Uneven and the default configuration selects both two structures.

According to these parameters, Approximate Code framework divides the data/parity nodes into several local stripes. Each local stripe has $n$ nodes,  
In a $n$-node stripe, $k$ of them are data nodes and $r=n-k$ nodes are local parity nodes.
Assume the ratio of important data is $1/h$, the framework utilizes $h$ local stripes to construct a global stripe, which includes $k*h$ data nodes and $r*h$ local parity nodes in total.
In a global stripe, $g$ additional nodes are designed for global parities, which are calculated by the important data, so the total number of nodes $N$ in APPR.CodeName ($k,r,g,h$) is
$N= h*(k+r) + g$.

Approximate Code guarantees that the unimportant data can tolerate any $r$ node failures and the important data can tolerate any $r+g$ node failures.
Since the 3DFTs is a typical configuration, we mainly discuss the situation of $r+g=3$ in the rest of our paper, so $r$ is usually $1$ or $2$.%, except section \ref{appr-rsbased}.

\subsection{Approximate RS-based Codes}\label{appr-rsbased}
The operation of RS($k,m$) is based on the GF, which provides $m$ independent horizontal parities for $k$ data nodes. Therefore, the code segmentation for RS is arbitrary, that is, it supports any $r=p-g(0<g<m)$. RS also supports both two structures. We then introduce the construction of Approximate RS Code and Approximate LRC.

\subsubsection{Approximate RS Code}
We consider the inputted erasure code as RS($4,3$), as shown in Figure \ref{fig-RS-2}. Three horizontal parities are divided into one local and two global parities with the Uneven structure and it generate Approximate RS Code ($4,1,2,3$,Uneven).
As a result, the unimportant data and their corresponding parities constitutes a RS ($4,1$) array, and the important data and their corresponding parities form a RS($4,3$).

\subsubsection{Approximate LRC}

\begin{figure}
    \centering
    \subfigure[The generation of APPR.RS Code]{
        \includegraphics[width=0.8\linewidth]{photo/RS-2.pdf}\label{fig-RS-2}
    }

    \subfigure[The generation of APPR.LRC]{
        \includegraphics[width=0.8\linewidth]{photo/LRC-2.pdf}\label{fig-LRC-2}
    }
    \caption{The construction and the encoding process of APPR.RS ($4,1,2,3$)}
\end{figure}

\subsection{Approximate XOR-based Codes}\label{APPRXOR}
Since we mainly provide 3DFTs for important data, we prefer to construct Approximate Code with several XOR-based codes to provide faster encoding and reconstruction speed than RS-based codes. Here we introduce two typical construction of Approximate XOR-based codes, Approximate STAR Code and Approximate TIP-Code.

@@

\subfigure[Generation process]{
    \label{fig-ap-tip-GEN}
    \includegraphics[width = \linewidth]{photo/APPR-STAR-GEN.pdf}
}
\caption{The construction and the encoding process of APPR.STAR ($5,2,1,4$,Uneven)}
\label{fig-appr-star}
\end{figure}

\subsubsection{Approximate STAR Code}
Figure \ref{fig-appr-star} shows the construction and the encoding process of APPR.STAR($5,2,1,4$,Uneven).
As introduced in \ref{existEC}, STAR Code \cite{STAR} has 3 parity chunks and it is a tipical 3DFTs XOR-based erasure code.
Since STAR is a direct extension of EVENODD\cite{EVENODD}, that is to say, STAR code that removes the anti-diagonal parity is the typical RAID-6 code EVENODD. As shown in Figure \ref{fig-appr-star}, in this case, the horizontal and diagonal parity are used as local parities while the anti-diagonal parity is defined as global parity.
According to the construction requirements of STAR, each node is divided into 4 blocks.

@@

\begin{table}[htb]
\centering
\caption{Comparison of storage overhead, fault tolerance and average single write performance between RS, LRC, STAR, TIP, Approximate RS, Approximate STAR and Approximate TIP, where $p$ is a prime number.}\label{tab-properties}
\begin{tabular}{|c|c|c|c|}
\hline
EC & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}Fault\\ Tolerance\end{tabular} & \begin{tabular}[c]{@{}c@{}}Ave Single Write\\ Overhead \end{tabular} \\ \hline
RS($k,r$) & $(k+r)/k$ & $r$ & $r+1$ \\ \hline
STAR($p$) & $(p+3)/p$ & $3$ & $6-\frac{4}{p}$ \\ \hline
TIP-code($p$) & $\frac{p+1}{P-2}$ & $3$ & 4 \\ \hline
\begin{tabular}[c]{@{}c@{}}APPR.RS\\ ($k,r,g,h$)\end{tabular} & \multirow{3}{*}{$\frac{(k+r)h+g}{kh}$} & $r+g$ & $1+r+\frac{g}{h}$ \\ \cline{1-1} \cline{3-4}
\begin{tabular}[c]{@{}c@{}}APPR.STAR\\ ($k,2,1,h$)\end{tabular} &  & 3 & $2\frac{k-h-1}{kh}+4$ \\ \cline{1-1} \cline{3-4}
\begin{tabular}[c]{@{}c@{}}APPR.TIP\\ ($k,1,2,h$)\end{tabular} &  & 3 & $2+\frac{2}{h}$ \\ \hline
\end{tabular}
\end{table}

@@

In the first part, we compared the decoding/encoding/recovery time, Storage Efficiency, Fault Tolerance and Single Write(update) Cost of Approximate Code with several 3DFTs erasure codes, including RS code, LRC, STAR and TIP code. Experiments as well as mathematical analysis are used to demonstrate the performance of Approximate Code.

In the second part, we use the latest interpolation algorithm to simulate the approximate recovery and fuzzification process in a data corruption scenario to prove that the lost of unimportant data is acceptable.

\subsubsection{Metrics}
We use the \textbf{Storage Efficiency}, \textbf{Fault Tolerance} and \textbf{Single Write(update) Cost} defined in Table \ref{tab-properties} as mathematical metrics.

We use \textbf{Encoding Time}, \textbf{Recovery Time} and \textbf{Decoding Time} as the metrics in our experiments. Encoding Time is the time for generating all parity nodes and decoding time is the computation time for recovering the lost nodes. Note that the Approximate Code can only recover important data in some cases, and we don't consider the recovery of non-critical data, so the Approximate Code may recover less data than other codes. Recovery time consists of computation time, I/O overhead and transmission time
\subsubsection{Experiments Environment}
The environment of our experiments are shown in Table \ref{tab-platform}. We set a Hadoop system with one NameNode and $h$ DataNodes. Each DataNodes storage the data of one layer of Approximate Code and the global parities are distributed at each DataNodes. We set $h=4,6$ and node size equal $1GB$ here as two default configurations.Our experiment can mainly be divided into four cases. First, we evaluate the encoding time for several erasure codes. We then evaluate the decoding time of the scenarios where single, double and triple nodes are corrupted.

we performed the experiment of video frame recovery with the frame interpolation technique. The dataset we used is a collection of 60fps videos from \textbf{YouTube-8m} \cite{youtube8m}. We simulated a 1\% data loss\footnote{In a distributed system, a single video can be stored in dozens or even hundreds of nodes. We assume that its important data is recovered, while the loss of unimportant data accounts for 1\% of the total video size.} on the less important video frames and successfully recovered the lost ones, although the recovered frames have some discrepancies with the original data. The average quality of the recovered pictures is commonly above 35dB in terms of Peak Signal to Noise Ratio PSNR .
